Mixture Modeling Paper Results

### 2017-03-22 PaperEx170308.Rmd
Cleaned data (removed duplicates), updated cutoff algorithm, and updated analyses for paper

#Runs loops of mixture model over different numbers of components and the normal and skew-normal distribution. This function accepts a data frame of the data and identifiers (variables must be entitled data and id respectively). This is the longest function to run and may fail, but can be re-run with adjustments using various options based on the error message output when the function fails. The default values are to do both skew-normal and normal approximation, with up to 5 components and 10 loops per combination of distribution and number of components. It is not reccommended to change these unless the default function fails.
#accepts a dataframe with columns id and data
fitloops<-function(datawithids,loops=10,maxcp=5){
  dists="Both"
  datawithids<-unique(datawithids)
  data<-datawithids$data
  datapts<-length(data)
  norms<-vector("list")
  errors<-matrix(0, nrow=maxcp, ncol=2)
  loopErr = function(data,i,j,family) {
    tryCatch(suppressWarnings(smsn.mix(data, nu =3, g = i, get.init = TRUE, criteria = TRUE, group = TRUE, family = family, calc.im=FALSE, obs.prob=TRUE, iter.max=5000, kmeans.param=list(iter.max = 50, n.start = 5))),
             error = function(e) {message(paste("Error in loop", j, "of", family, "with", i, "components", sep=" ")); 
               NA}) 
  }

@@

#examp1<-read.csv(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex1.csv", colClasses=c("NULL", NA, NA))

#hist(examp1$data, breaks=100, main="Histogram of Data")
#dens1<-density(examp1$data)
#plot(dens1, main="Density of Data")

#fitloopsobject<-fitloops(datawithids=examp2)
  #might not run due to 5 component solution not being easily optimized, if it doesn't run either load the full file, or run fitloopsobject<-fitloops(datawithids=examp2,maxcp=4): 
#load(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex1fitloops")

#bicgraph(model=fitloopsobject1)

#modelpickobject2<-modelpick(fitloopsobject1)

#rawuncertgraph(modelpickobject1)
#rawdistgraph(modelpickobject1)
#rawhistcuts(modelpickobject1)

@@

examp2<-read.csv(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex2.csv")

@@

summaryobject2<-summaryout(cutobj = cutoffobject2)
```

>>>>

#Runs loops of mixture model over different numbers of components and the normal and skew-normal distribution. This function accepts a data frame of the data and identifiers (variables must be entitled data and id respectively). This is the longest function to run and may fail, but can be re-run with adjustments using various options based on the error message output when the function fails. The default values are to do both skew-normal and normal approximation, with up to 5 components and 10 loops per combination of distribution and number of components. It is not reccommended to change these unless the default function fails.
#accepts a dataframe with columns id and data
fitloops<-function(datawithids,loops=10,maxcp=5){
  dists="Both"
  datawithids2<-unique(datawithids)
  if (nrow(unique(datawithids))!=nrow(datawithids)){
    stop("The input data (datawithids) must not include duplicates. Please remove duplicates.")
  }
  data<-datawithids$data
  datapts<-length(data)
  norms<-vector("list")
  errors<-matrix(0, nrow=maxcp, ncol=2)
  loopErr = function(data,i,j,family) {
    tryCatch(suppressWarnings(smsn.mix(data, nu =3, g = i, get.init = TRUE, criteria = TRUE, group = TRUE, family = family, calc.im=FALSE, obs.prob=TRUE, iter.max=5000, kmeans.param=list(iter.max = 50, n.start = 5))),
             error = function(e) {message(paste("Error in loop", j, "of", family, "with", i, "components", sep=" ")); 
               NA}) 
  }

@@

examp1<-read.csv(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex1.csv", colClasses=c("NULL", NA, NA))

hist(examp1$data, breaks=100, main="Histogram of Data")
dens1<-density(examp1$data)
plot(dens1, main="Density of Data")

#fitloopsobject1<-fitloops(datawithids=examp2)
  #might not run due to 5 component solution not being easily optimized, if it doesn't run either load the full file, or run fitloopsobject1<-fitloops(datawithids=examp2,maxcp=4): 
load(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex1fitloops")

bicgraph(fitobj=fitloopsobject1)

modelpickobject1<-modelpick(fitloopsobject1)

rawuncertgraph(modelpickobject1)
rawdistgraph(modelpickobject1)
rawhistcuts(modelpickobject1)

cutoffobject1<-cutoff(modelpickobj = modelpickobject1)

cutuncertgraph(cutobj = cutoffobject1)
cutdistgraph(cutobj = cutoffobject1)

summaryobject1<-summaryout(cutobj = cutoffobject1)
summaryobject1$outtab

@@

examp2<-read.csv(file="/Users/sarahsullivan/Documents/SullivanDocs/Rwd/cutoff/ex2.csv", stringsAsFactors = F, colClasses=c("NULL", NA, NA))
examp2<-examp2[,c("id", "data")]

@@

summaryobject2<-summaryout(cutobj = cutoffobject2)
summaryobject2$outtab
```
